---
title: "Students"
---

The project aims to reach 25-30 students per semester, from the spring semester of 2020 to the fall semester of 2022. 

WAV teams will comprise 4 or 5 data science students (most likely majoring in statistics and/or data science) and one community engagement concentrator. Funding of up to $2500 per student per semester is available, although the actual amount paid will vary based on regulations at your home institution. 

## Eligibility

Minimum requirements for data science students:

- has taken at least one course in computer programming
- has taken at least one course in statistics
- has taken at least one additional course in data science, data analysis, etc. 
- preferably a sophomore or junior
- ability to commit to 8-10 hours per week through the spring semester

Minimum requirements for community engagement students:

- has completed a community engagement course, or is enrolled in a related major, minor, or [concentration](https://www.smith.edu/academics/community-engagement-and-social-change-concentration), or the equivalent
- is a junior or senior
- ability to commit to 8-10 hours per week through the spring semester

Eligibility for [NSF funding](https://www.nsf.gov/pubs/forms/affidavit_eligibility_of_employment.pdf):

- US Citizen or permanent resident

If you are not eligible for NSF funding, please contact your home institution for additional funding options. You may still complete the application. 

```{r, include=FALSE, eval=FALSE}
icons::icon_save(
  list(linked_in = icons::fontawesome("linkedin")),
  path = "gfx"
)
```


```{r, include=FALSE}
library(tidyverse)
library(googlesheets4)
students <- read_sheet("1g3-V56CBijLJfPEvOfGo1ZShmGPfzrQDHe-lFG19FL0")
students <- students %>%
  mutate(
    Student = ifelse(!is.na(linkedin), paste0("[", name, "](", linkedin, ")"), name),
    Institution = stringr::str_to_title(institution)
  )
```


## Cohort 5

- Applications for Cohort 5 will be reviewed on a rolling basis, beginning **November 10th, 2021**. 


## Cohort 4

- Students selected for Cohort 4 will begin in the fall semester of 2021. 

- Applications for Cohort 4 will open on **March 12th, 2021**.

<div class="alert alert-info" role="alert">
`r icon::fa("bullhorn")` [**APPLY NOW**](https://forms.gle/CuXVD9xd66R6jUJW6)
</div>


## Cohort 3

- `r nrow(filter(students, cohort == 2))` students selected for Cohort 3 began in the spring semester of 2021. 

```{r, echo=FALSE}
students %>%
  filter(cohort == 3) %>%
  select(Student, Institution, role) %>%
  arrange(Institution, role, Student) %>%
  knitr::kable()
```


## Cohort 2

- `r nrow(filter(students, cohort == 2))` students selected for Cohort 2 began in the fall semester of 2020.

```{r, echo=FALSE}
students %>%
  filter(cohort == 2) %>%
  select(Student, Institution, role) %>%
  arrange(Institution, role, Student) %>%
  knitr::kable()
```



## Cohort 1

- `r nrow(filter(students, cohort == 1))` students selected for Cohort 1 began in the spring semester of 2020. 

```{r, echo=FALSE}
students %>%
  filter(cohort == 1) %>%
  select(Student, Institution, role) %>%
  arrange(Institution, role, Student) %>%
  knitr::kable()
```


